Simple connectome inference from partial correlation statistics in calcium imaging

### 2014-06-27 article.tex
add

\jmlrauthors{A. Sutera et al}
% \shortauthor{A. Sutera et al.}

@@

\begin{table}[t]\label{tab:comparison}
%\caption{Evaluation of different methods on the four \textit{normal} datasets\label{tab:comparison}}
\centering
\small
\begin{tabular}{| l | c c c c | c c c c |}
\hline
& \multicolumn{4}{c|}{AUROC} & \multicolumn{4}{c|}{AUPRC} \\
\textit{Method} $\backslash$ \textit{normal-} & \textit{1} & \textit{2} & \textit{3} & \textit{4} & \textit{1} & \textit{2} & \textit{3} & \textit{4} \\
\hline
\hline
No  filtering       					& 0.777 & 0.767 & 0.772 & 0.774 & 0.070 & 0.064 & 0.068 & 0.072\\
$ h \circ g \circ f_1$                  & 0.923 & 0.925 & 0.923 & 0.922 & 0.311 & 0.315 & 0.313 & 0.304\\
$ w \circ h \circ g \circ f_1$          & 0.931 & 0.929 & 0.928 & 0.926 & 0.326 & 0.323 & 0.319 & 0.303\\
+ PCA         							& 0.932 & 0.930 & 0.928 & 0.926 & 0.355 & 0.353 & 0.350 & 0.333\\
Averaging           					& 0.937 & 0.935 & 0.935 & 0.931 & 0.391 &  0.390 &  0.385 & 0.375\\
Full method           					& 0.943 & 0.942 & 0.942 & 0.939 & 0.403 & 0.404 & 0.398 & 0.388\\
\hline
PC & 0.886 & 0.884 & 0.891 &  0.877 & 0.153 & 0.145 & 0.170 & 0.132\\
GTE & 0.890 & 0.893 & 0.894 & 0.873 & 0.171 & 0.174 & 0.197 & 0.142\\
GENIE3 & \textcolor{red}{?} & & & & & & & \\
\hline
\end{tabular}
\caption{Top: Performance on \textit{normal-1,2,3,4} with partial correlation and different filtering functions.
Bottom: Performance on \textit{normal-1,2,3,4} with different methods.}
\end{table}

@@

The fact that our method is unable to predict edge directions does not seem to
be a disadvantage with respect to GTE and GENIE3. Although partial correlation
scores each edge and its opposite similarly, it can reach precision values
higher than 0.5 (see Figure \ref{fig:curves}(b)), suggesting that it mainly ranks high
pairs of neurons that interact in both directions.  It is interesting also to
note that, on \textit{normal-2}, a method that perfectly predicts the
undirected network (i.e., that gives a score of $1$ to each pair $(i,j)$ such that
$(i,j)\in E$ or $(j,i)\in E$, and $0$ otherwise) already reaches an AUROC as high
as $0.995$ and an AUPRC of $0.789$.

@@

Theses filters lead, taken individually, to worse performances
 than filters $f_1$ and
$f_2$ but the averaging approach over all low-pass
filters gets better \textcolor{red}{AS:Does it necessary to show it numerically?}.

@@

\begin{table}[t]\label{tab:comparison}
%\caption{Evaluation of different methods on the four \textit{normal} datasets\label{tab:comparison}}
\centering
\small
\begin{tabular}{| l | c c c c c c | c c c c c c|}
\hline
& \multicolumn{4}{c|}{AUROC} & \multicolumn{4}{c|}{AUPRC} \\
\textit{Method} $\backslash$ \textit{normal-} & \textit{lowcon} & \textit{highcon} & \textit{lowcc} & \textit{highcc} & \textit{normal-3-highrate} & \textit{normal-4-lownoise} & \textit{1} & \textit{2} & \textit{3} & \textit{4} & \textit{normal-3-highrate} & \textit{normal-4-lownoise}\\
\hline
\hline
% No  filtering       					& 0.777 & 0.767 & 0.772 & 0.774 & 0.070 & 0.064 & 0.068 & 0.072\\
% $ h \circ g \circ f_1$                  & 0.923 & 0.925 & 0.923 & 0.922 & 0.311 & 0.315 & 0.313 & 0.304\\
% $ w \circ h \circ g \circ f_1$          & 0.931 & 0.929 & 0.928 & 0.926 & 0.326 & 0.323 & 0.319 & 0.303\\
% + PCA         							& 0.932 & 0.930 & 0.928 & 0.926 & 0.355 & 0.353 & 0.350 & 0.333\\
% Averaging           					& 0.937 & 0.935 & 0.935 & 0.931 & 0.391 &  0.390 &  0.385 & 0.375\\
% Full method           					& 0.943 & 0.942 & 0.942 & 0.939 & 0.403 & 0.404 & 0.398 & 0.388\\
% \hline
% PC & 0.886 & 0.884 & 0.891 &  0.877 & 0.153 & 0.145 & 0.170 & 0.132\\
% GTE & 0.890 & 0.893 & 0.894 & 0.873 & 0.171 & 0.174 & 0.197 & 0.142\\
% GENIE3 & & & & & & & & \\
% \hline
\end{tabular}
\caption{Top: Performance on \textit{normal-1,2,3,4} with partial correlation and different filtering functions.
Bottom: Performance on \textit{normal-1,2,3,4} with different methods.}
\end{table}

>>>>

% \jmlrauthors{A. Sutera et al}
% \shortauthor{A. Sutera et al.}

@@

\begin{table}[t]\label{tab:comparison}
%\caption{Evaluation of different methods on the four \textit{normal} datasets\label{tab:comparison}}
\centering
\small
\begin{tabular}{| l | c c c c | c c c c |}
\hline
& \multicolumn{4}{c|}{AUROC} & \multicolumn{4}{c|}{AUPRC} \\
\textit{Method} $\backslash$ \textit{normal-} & \textit{1} & \textit{2} & \textit{3} & \textit{4} & \textit{1} & \textit{2} & \textit{3} & \textit{4} \\
\hline
\hline
No  filtering       					& 0.777 & 0.767 & 0.772 & 0.774 & 0.070 & 0.064 & 0.068 & 0.072\\
$ h \circ g \circ f_1$                  & 0.923 & 0.925 & 0.923 & 0.922 & 0.311 & 0.315 & 0.313 & 0.304\\
$ w \circ h \circ g \circ f_1$          & 0.931 & 0.929 & 0.928 & 0.926 & 0.326 & 0.323 & 0.319 & 0.303\\
+ PCA         							& 0.932 & 0.930 & 0.928 & 0.926 & 0.355 & 0.353 & 0.350 & 0.333\\
Averaging           					& 0.937 & 0.935 & 0.935 & 0.931 & 0.391 &  0.390 &  0.385 & 0.375\\
Full method           					& 0.943 & 0.942 & 0.942 & 0.939 & 0.403 & 0.404 & 0.398 & 0.388\\
\hline
PC & 0.886 & 0.884 & 0.891 &  0.877 & 0.153 & 0.145 & 0.170 & 0.132\\
GTE & 0.890 & 0.893 & 0.894 & 0.873 & 0.171 & 0.174 & 0.197 & 0.142\\
GENIE3 & 0.892 & 0.891 & 0.887 & 0.887 & 0.232 & 0.221 & 0.237 & 0.215 \\
\hline
\end{tabular}
\caption{Top: Performance on \textit{normal-1,2,3,4} with partial correlation and different filtering functions.
Bottom: Performance on \textit{normal-1,2,3,4} with different methods.}
\end{table}

@@

The fact that our method is unable to predict edge directions does not seem to
be a disadvantage with respect to GTE and GENIE3. Although partial correlation
scores each edge and its opposite similarly, it can reach precision values
higher than 0.5 (see Figure \ref{fig:curves}(b)), suggesting that it ranks high
mainly pairs of neurons that interact in both directions (there are about XX\%
of such pairs in the \textit{normal-2} network). %% It is interesting also to note
%% that, on \textit{normal-2}, a method that perfectly predicts the undirected
%% network (i.e. that gives a score of 1 to each pair $(i,j)$ such that $(i,j)\in
%% V$ or $(j,i)\in V$, 0 otherwise) can reach an AUROC of $0.995$, which does not
%% leave much room for improvement by predicting edge directionality. The AUPRC on
%% the other hand would be 0.789 and thus be more sensitive to the prediction of
%% edge directions.

@@

Theses filters lead, taken individually, to worse performances
 than filters $f_1$ and
$f_2$ but the averaging approach over all low-pass
filters gets better.

\begin{table}[ht]\label{tab:comparison}
%\caption{Evaluation of different methods on the four \textit{normal} datasets\label{tab:comparison}}
\centering
\small
\begin{tabular}{| l | c c c c | c c c c |}
\hline
& \multicolumn{4}{c|}{AUROC} & \multicolumn{4}{c|}{AUPRC} \\
\textit{Method} $\backslash$ \textit{normal-} & \textit{1} & \textit{2} & \textit{3} & \textit{4} & \textit{1} & \textit{2} & \textit{3} & \textit{4} \\
\hline
\hline
Partial correlation ($f_1$ + $f_2$) & 0.937 & 0.935 & 0.935 & 0.931 & 0.391 &  0.390 &  0.385 & 0.375  \\
Partial correlation ($f_1$ + $f_2$ + $f_3$ + $f_4$) & \textbf{0.938} & \textbf{0.936} & \textbf{0.936} & \textbf{0.932} & 0.391 & 0.389 & 0.385 & 0.374\\
\hline
\end{tabular}
\caption{Performance on \textit{normal-1,2,3,4} with partial correlation with different averaging approaches.}
\end{table}

@@

\begin{table}[h]\label{tab:comparison_extended}
\centering
\small
\begin{tabular}{| l | c c c c c c |}
\hline
& \multicolumn{6}{c|}{AUROC}\\
\textit{Method} $\backslash$ \textit{normal-} & \textit{lowcon} & \textit{highcon} & \textit{lowcc} & \textit{highcc} & \textit{3-highrate} & \textit{4-lownoise} \\
\hline
\hline
& \\ \hline
& \multicolumn{6}{c|}{AUROC}\\ \hline
& \\
\end{tabular}
\caption{Top: Performance on \textit{normal-1,2,3,4} with partial correlation and different filtering functions.
Bottom: Performance on \textit{normal-1,2,3,4} with different methods.}
\end{table}

\begin{table}[t]\label{tab:comparison}
%\caption{Evaluation of different methods on the four \textit{normal} datasets\label{tab:comparison}}
\centering
\small
\begin{tabular}{| l | c c c c c c | c c c c c c|}
\hline
& \multicolumn{6}{c|}{AUROC} & \multicolumn{6}{c|}{AUPRC} \\
\textit{Method} $\backslash$ \textit{normal-} & \textit{lowcon} & \textit{highcon} & \textit{lowcc} & \textit{highcc} & \textit{3-highrate} & \textit{4-lownoise} & \textit{lowcon} & \textit{highcon} & \textit{lowcc} & \textit{highcc} & \textit{3-highrate} & \textit{4-lownoise}\\
\hline
\hline
% No  filtering       					& 0.777 & 0.767 & 0.772 & 0.774 & 0.070 & 0.064 & 0.068 & 0.072\\
% $ h \circ g \circ f_1$                  & 0.923 & 0.925 & 0.923 & 0.922 & 0.311 & 0.315 & 0.313 & 0.304\\
% $ w \circ h \circ g \circ f_1$          & 0.931 & 0.929 & 0.928 & 0.926 & 0.326 & 0.323 & 0.319 & 0.303\\
% + PCA         							& 0.932 & 0.930 & 0.928 & 0.926 & 0.355 & 0.353 & 0.350 & 0.333\\
% Averaging           					& 0.937 & 0.935 & 0.935 & 0.931 & 0.391 &  0.390 &  0.385 & 0.375\\
% Full method           					& 0.943 & 0.942 & 0.942 & 0.939 & 0.403 & 0.404 & 0.398 & 0.388\\
% \hline
% PC & 0.886 & 0.884 & 0.891 &  0.877 & 0.153 & 0.145 & 0.170 & 0.132\\
% GTE & 0.890 & 0.893 & 0.894 & 0.873 & 0.171 & 0.174 & 0.197 & 0.142\\
% GENIE3 & & & & & & & & \\
% \hline
\end{tabular}
\caption{Top: Performance on \textit{normal-1,2,3,4} with partial correlation and different filtering functions.
Bottom: Performance on \textit{normal-1,2,3,4} with different methods.}
\end{table}
